%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Amirhessam Tahmassebi - CV - March 2024
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{template}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% \namesection{Firstname}{Lastname}{ \urlstyle{same}\url{http://example.com} \\
% \href{mailto:user@example.com}{user@example.com} | 123.456.7890
% }

% \href{http://linkedin.com/in/12346}{http://linkedin.com/in/12346}

\namesection{Amirhessam}{Tahmassebi}{ % Your name

\href{mailto:atahmassebi@fsu.edu}{Email: atahmassebi@fsu.edu} | Phone: (330) 606-7855 \\ % Your contact information
% Your website, LinkedIn profile or other web address

LinkedIn:// \href{https://www.linkedin.com/in/amirhessam}{\bf amirhessam} |
WebSite:// \href{http://amirhessam.com}{\bf amirhessam.com} |
Github:// \href{https://github.com/amirhessam88}{\bf amirhessam88} \\
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\section{Education} 
\sectionsep
\runsubsection{Florida State University}
\descript{PhD in Computational Science}
\location{Aug 2018 | Tallahassee, FL \textbullet{} Cum. GPA: 3.969/4.0 \textbullet{} Advisor: \textbf{\href{https://people.sc.fsu.edu/~ameyerbaese/}{Dr. Anke Meyer-Baese}}}


\sectionsep
\runsubsection{Florida State University}
\descript{MSc in Computational Science}
\location{Dec 2017 | Tallahassee, FL \textbullet{} Cum. GPA: 3.969/4.0 \textbullet{} Advisor: \textbf{\href{https://people.sc.fsu.edu/~ameyerbaese/}{Dr. Anke Meyer-Baese}}}

\sectionsep% Some whitespace after the section

\runsubsection{University of Akron}
\descript{MSc in Physics}
\location{Aug 2015 | Akron, OH   \textbullet{} Cum. GPA: 3.982/4.0  \textbullet{} Advisor: \textbf{\href{https://www.uakron.edu/physics/faculty-staff/bio-detail.dot?u=buldum}{Dr. Alper Buldum}}}

\sectionsep% Some whitespace after the section

\runsubsection{University of Tehran}
\descript{BSc in Physics}
\location{July 2010 | Tehran, Iran  \textbullet{} Cum. GPA: 3.1/4.0  \textbullet{} Advisor: \textbf{\href{http://physics.ut.ac.ir/~moshfegh/}{Dr. Hamidreza Moshfegh}}}

\sectionsep% Some whitespace after the section
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \begin{center}
% \huge\color{subheadings}\custombold{LIFELONG LEARNER}
% \end{center}
% \hline
\sectionsep
\section{Working Experience: Industry}

\sectionsep
\runsubsection{Rivian and Volkswagen Group Technologies}
\descript{| Senior Data Scientist - Algorithms}

\location{November 2024 – Present | Remote}
\vspace{\topsep}

\begin{tightemize}
\item Technical Lead of main design patterns as part of the Insights Team to create scalable solutions within Datarbicks platform for all users within Rivian-VW Join-Venture.

\item Tools: Python, Terraform, Databricks, Git, GitLab.
\end{tightemize}
\sectionsep

\sectionsep
\runsubsection{Rivian Automotive}
\descript{| Senior Data Scientist - Algorithms}

\location{September 2021 – November 2024 | Remote}
\vspace{\topsep}

\begin{tightemize}
\item Technical Lead of the Algorithms to Deliver Automated Decision-Making Platform and Overall Data System Architecture for Factory Data and Various Scalable Solutions within Manufacturing Engineering.

\item Tools: Python, SQL, Pandas, dbt. Scikit-Learn, ZenML, MLFlow, Kubeflow, Git, GitLab.
\end{tightemize}
\sectionsep


\sectionsep
\runsubsection{ExxonMobil Corporation}
\descript{| Senior Data Scientist}

\location{January 2020 – September 2021 | Houston, TX}
\vspace{\topsep}

\begin{tightemize}
\item Lead in the design, development, and implementation of an Attrition model for the Polyethylene (PE) sector of the EMCC to predict the customer churn with statistical significance in the future months with the hope to incorporate better solutions for negotiations of the new contracts with customers due to unprecedented things such as low demand and COVID19.

\item  Lead in the design, development, and implementation of the interpretable Transaction-Specific-Pricing model for Polypropylene (PP) sector to apply customer segmentation using clustering algorithms and machine learning and recommend pricing to maximize the variable margin for each month of revenue for Americas (Canada, USA, and Mexico).

\item Lead in the design, development, and implementation of the interpretable Rules-Based model for High Density Polyethylene (HDPE) and Linear Low Density Polyethylene (LLDPE) sectors to incorporate customer segmentation and recommend pricing to maximize the variable margin for each month of revenue for CANUSA (Canada and USA).

\item Tools: Python, SQL, Pandas, Scikit-Learn, XGBoost, GLM-Net, TensorFlow, Keras, Azure DevOps, Git, GitHub.
\end{tightemize}
\sectionsep


\sectionsep
\runsubsection{Cerner Corporation}
\descript{| Data Scientist}

\location{October 2018 – December 2019 | Kansas City, MO}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Building 90-day pediatric asthma re-admission model for Children's Hospital of Orange County (CHOC).
\item Building 30-day pediatric all cause re-admission model for 17 hospitals around the US.
\item Building predictive model for bundled payments care improvement advanced (BPCI-A) for 37 defined CMS episodes for Navi-Health.
\item Tools: Python, Spark, SQL, MLlib, Pandas, Scikit-Learn, XGBoost, GLM-Net, TensorFlow, Keras, AWS, JIRA, Git, GitHub.
\end{tightemize}
\sectionsep
\sectionsep

\sectionsep
\runsubsection{Mynomx Inc. (Previously Precision Wellness Inc.)}
\descript{| Data Scientist}

\location{June 2017 – August 2017, May 2018 – August 2018 | Palo Alto, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developed Machine Learning algorithms for population health management on Stanford and UK Bio-Bank databases.
\item Took statistical models and transformed them into robust and scalable codes using Spark and ML library.
\item Performed integration of the algorithms and data sources.
\item Implemented new codes at scale and to meet performance guidelines.
\item Tools: Python, R, Spark, Scikit-Learn, Cox Regression, TensorFlow, Keras, Lifelines, MLlib, BitBucket, JIRA, Apache Zeppelin.

\end{tightemize}


\sectionsep
\section{Working Experience: Academic}
\sectionsep

\runsubsection{Florida State University}
\descript{| Graduate Teaching Assistant}

\location{August 2015 – May 2018 | Tallahassee, FL}
\vspace{\topsep}
\begin{tightemize}
\item Developed an under-graduate level course in High Performance Computing including OpenMP, MPI, CUDA, and OpenACC programming.
\item Working with \textbf{\href{https://pic.fsu.edu/}{Programs in Interdisciplinary Computing (PIC)}} at Florida State University as an Instructor for Spreadsheets in Business (CGS 2518). 
\end{tightemize}

\sectionsep

\runsubsection{The University of Akron}
\descript{| Graduate Teaching Assistant}

\location{August 2013 – August 2015 | Akron, OH}
\begin{tightemize}
\item Worked in Physics (I , II) LABS.
\item Instructor for Physics Life Science.
\item Grader for Astro-Physics \& Classical Physics (I , II) .
\end{tightemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\sectionsep
\section{University Appointments}

\sectionsep
\runsubsection{Department of Scientific Computing, Florida State University}
\descript{| Affiliated Faculty}

\location{October 2018 – Present | Tallahassee, FL}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Leading Dr. Meyer-Baese's group and directing the MS and PhD students.
\item Collaborating on different projects including deep learning in medical imaging, network analysis, and machine learning.
\end{tightemize}

\sectionsep
\runsubsection{School of Information, Florida State University}
\descript{| Adjunct Professor}

\location{August 2022 – Present | Tallahassee, FL}
\vspace{\topsep} 
\begin{tightemize}
\item Fall 2022: Data Mining and Analytics (LIS 5765)
\item Summer 2023: Data Mining and Analytics (LIS 5765)
\item Fall 2023: Data Mining and Analytics (LIS 5765)
\item Fall 2023: Data Mining and Analytics (LIS 4761)
\item Summer 2024: Data Mining and Analytics (LIS 5765)
\end{tightemize}


\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Editorial Board}

\runsubsection{Journal of Frontiers in Neuroinformatics}
\descript{| Associate Editor}
\location{August 2021 – Present}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
% \hline
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\section{Research}
\sectionsep
\runsubsection{Florida State University}
\location{August 2015 – August 2018 | Tallahassee, FL}
Working on a Data Mining Project under supervision of  \textbf{\href{https://people.sc.fsu.edu/~ameyerbaese/}{Dr. Anke Meyer-Baese}} to apply Machine Learning algorithms on fMRI and MRI data. I am also working on Deep Learning algorithms to build predictive models for various databases in collaboration on several fields including neuro-imaging, breast cancer, dementia, energy consumption, stock market, ground motion modeling, airfoil noise, distance-learning, and engineering problems.

\sectionsep

\runsubsection{The University of Akron}
\location{August 2013 – August 2015 | Akron, OH}
Worked with \textbf{\href{https://www.uakron.edu/physics/faculty-staff/bio-detail.dot?u=buldum}{Dr. Alper Buldum}} for two years. My Thesis topic was Fluid Flow Through Carbon Nanotubes \& Graphene Based Nanostructures. We implemented a Molecular Dynamics code written in Fortran for three different models, containing Single-Walled Carbon Nanotubes, Graphene Wall as structures, and Liquid Argon as flow of the system. The application of that would be found in the field of Drug Delivery.
\sectionsep
\hline
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\section{Python Libraries}
\sectionsep
\runsubsection{SlickML}
\location{August 2020 – Present}
\textbf{\href{https://github.com/slickml/slick-ml}{SlickML}} is an open-source machine learning library written in Python aimed at accelerating the experimentation time for a ML application. Data Scientist tasks can often be repetitive such as feature selection, model tuning, or evaluating metrics for classification and regression problems. SlickML provides Data Scientists with a toolbox of utility functions to quickly prototype solutions for a given problem with minimal code. More details on SlickML GitHub page at \custombold{\href{https://github.com/slickml/slick-ml}{https://github.com/slickml/slick-ml}} and SlickML docs at \custombold{\href{https://docs.slickml.com}{https://docs.slickml.com}}.


\sectionsep
\hline
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\section{Publications}
\sectionsep
\runsubsection{Book Chapters \& Theses}
\sectionsep
\begin{itemize}

\item Mohebali, B., \custombold{Tahmassebi, A.}, Meyer-Baese, A., \& Gandomi, A. H. (2020). Probabilistic neural networks: a brief overview of theory, implementation, and application. In Handbook of Probabilistic Models (pp. 347-367). Butterworth-Heinemann.

\item \custombold{Tahmassebi, A.}, \& Gandomi, A. H. (2018). Genetic programming based on error decomposition: A big data approach. In Genetic Programming Theory and Practice XV (pp. 135-147). Springer, Cham.


\item \custombold{Tahmassebi, A.}, (2018). Pattern Recognition in Medical Imaging: Supervised Learning of fMRI \& MRI Data (Doctoral dissertation, Florida State University).

\item \custombold{Tahmassebi, A.}, (2015). Fluid Flow Through Carbon Nanotubes And Graphene Based Nanostructures (Master thesis, University of Akron).


\end{itemize}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionsep 
\runsubsection{Journal Articles}
\begin{itemize}

\item Moradi Amani, A., \custombold{Tahmassebi, A.}, Stadlbauer, A., Meyer-Baese, U., Noblet, V., Blanc, F., \& Meyer-Baese, A. (2024). Controllability of Functional and Structural Brain Networks. Complexity, 2024(1), 7402894.    

\item Karbassiyazdi, E., Fattahi, F., Yousefi, N., \custombold{Tahmassebi, A.}, Taromi, A. A., Manzari, \& Razmjou, A. (2022). XGBoost model as an efficient machine learning approach for PFAS removal: Effects of material characteristics and operation conditions. Environmental Research.

\item Telikani, A., \custombold{Tahmassebi, A.}, Banzhaf, W., \& Gandomi, A. H. (2021). Evolutionary machine learning: A survey. ACM Computing Surveys.

\item \custombold{Tahmassebi, A.}, Motamedi, M., Alavi, A. H., \& Gandomi, A. H. (2021). An explainable prediction framework for engineering problems: case studies in reinforced concrete members modeling. Engineering Computations.

\item Meyer-Baese, A., Morra, L., \custombold{Tahmassebi, A.}, Lobbes, M., Meyer-Baese, U., \& Pinker, K. (2021). AI-Enhanced Diagnosis of Challenging Lesions in Breast MRI: A Methodology and Application Primer. Journal of Magnetic Resonance Imaging.

\item \custombold{Tahmassebi, A.}, Mohebali, B., Meyer-Baese, A., \& Gandomi, A. H. (2020). Multiobjective genetic programming for reinforced concrete beam modeling. Applied AI Letters, 1(1), e9.

\item \custombold{Tahmassebi, A.}, Wengert, G. J., Helbich, T. H., Bago-Horvath, Z., Alaei, S., Bartsch, R., \& Morris, E. A. (2018). Impact of Machine Learning With Multiparametric Magnetic Resonance Imaging of the Breast for Early Prediction of Response to Neoadjuvant Chemotherapy and Survival Outcomes in Breast Cancer Patients. Investigative Radiology.

\item \custombold{Tahmassebi, A.}, Gandomi, A. H., Fong, S., Meyer-Baese, A., \& Foo, S. Y. (2018). Multi-stage optimization of a deep model: A case study on ground motion modeling. PloS one, 13(9), e0203829.


\item \custombold{Tahmassebi, A.}, Gandomi, A. H., Schulte, M. H., Goudriaan, A. E., Foo, S. Y., \& Meyer-Baese, A. (2018). Optimized Naive-Bayes and Decision Tree Approaches for fMRI Smoking Cessation Classification. Complexity, 2018.


\item \custombold{Tahmassebi, A.}, \& Gandomi, A. H. (2018). Building energy consumption forecast using multi-objective genetic programming. Measurement, 118, 164-171.


\item \custombold{Tahmassebi, A.}, Gandomi, A. H., \& Meyer-Baese, A. (2018). Stock Risk Assessment via Multi-Objective Genetic Programming. Journal of Postdoctoral Research, 6(3).


\item \custombold{Tahmassebi, A.}, Pinker-Domenig, K., Wengert, G., Helbich, T., Bago-Horvath, Z., \& Meyer-Baese, A. (2018). Determining the importance of parameters extracted from multi-parametric mri in the early prediction of the response to neo-adjuvant chemotherapy in breast cancer. Medical Imaging.

\item \custombold{Tahmassebi, A.}, Gandomi, A. H., McCann, I., Schulte, M. H., Schmaal, L., Goudriaan, A. E., \& Meyer-Baese, A. (2017). fMRI Smoking Cessation Classification. IEEE Transactions on Cybernetics.


\end{itemize}
\sectionsep 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionsep 
\runsubsection{Conference Articles}
\sectionsep
\begin{itemize}

\item \custombold{Tahmassebi, A.}, Mueller, K., Meyer-Baese, U., Munilla, J., Ortiz, A., \& Meyer-Baese, A. (2022, April). Graph signal processing to identify biomarkers in brain networks in dementia. In Medical Imaging 2022: Biomedical Applications in Molecular, Structural, and Functional Imaging (Vol. 12036, pp. 322-326). SPIE.

\item \custombold{Tahmassebi, A.}, Meyer-Baese, U., \& Meyer-Baese, A. (2021, November). Structural Target Controllability of Brain Networks in Dementia. In 2021 43rd Annual International Conference of the IEEE Engineering in Medicine \& Biology Society (EMBC) (pp. 3978-3981). IEEE.

\item Mohebali, B., Karbaschi, G., \custombold{Tahmassebi, A.}, Meyer-Baese, A., \& Gandomi, A. H. (2021, June). An Evolutionary Framework for Real-Time Fraudulent Credit Detection. In 2021 IEEE Congress on Evolutionary Computation (CEC) (pp. 1999-2006). IEEE.

\item \custombold{Tahmassebi, A.}, Karbaschi, G., Meyer-Baese, U., \& Meyer-Baese, A. (2021, April). Large-scale dynamical graph networks applied to brain cancer image data processing. In Computational Imaging VI (Vol. 11731, p. 1173104). International Society for Optics and Photonics.

\item \custombold{Tahmassebi, A.}, Karbaschi, G., Meyer-Baese, U., \& Meyer-Baese, A. (2021, April). Modeling disease agents transmission dynamics in dementia on heterogeneous spatially embedded networks. In Pattern Recognition and Tracking XXXII (Vol. 11735, p. 117350N). International Society for Optics and Photonics.


\item Van Popering, L., \custombold{Tahmassebi, A.}, Meyer-Baese, U., Dryba, M., Munilla, J., Ortiz, A., \& Meyer-Baese, A. (2021, February). Identifying the diffusion source of dementia spreading in structural brain networks. In Medical Imaging 2021: Biomedical Applications in Molecular, Structural, and Functional Imaging (Vol. 11600, p. 116000A). International Society for Optics and Photonics.

\item \custombold{Tahmassebi, A.}, Martin, J., Meyer-Baese, A., \& Gandomi, A. H. (2020, December). An Interpretable Deep Learning Framework for Health Monitoring Systems: A Case Study of Eye State Detection using EEG Signals. In 2020 IEEE Symposium Series on Computational Intelligence (SSCI) (pp. 211-218). IEEE.

\item \custombold{Tahmassebi, A.}, Meyer-Baese, U., \& Meyer-Baese, A. (2020, May). Modeling disease spreading process induced by disease agent mobility in Dementia networks. In Pattern Recognition and Tracking XXXI (Vol. 11400, p. 114000E). International Society for Optics and Photonics.

\item Meyer-Baese, L., Saad, F., \& \custombold{Tahmassebi}, A. (2020, February). Controllability of structural brain networks in dementia. In Medical Imaging 2020: Biomedical Applications in Molecular, Structural, and Functional Imaging (Vol. 11317, p. 113171W). International Society for Optics and Photonics.

\item Nagasubramanian, G., Sakthivel, R. K., Patan, R., Ehtemami, A., Meyer-Baese, \custombold{A., Tahmassebi}, A., \& Gandomi, A. H. (2020, April). Detection and isolation of black hole attack in mobile ad-hoc networks-a review. In Disruptive Technologies in Information Sciences IV (Vol. 11419, p. 114190N). International Society for Optics and Photonics.

\item Meyer-Baese, A., Foo, S., \custombold{Tahmassebi, A.}, Meyer-Baese, U., Amani, A. M., Götz, T., \& Pinker, K. (2020, May). Large-scale graph networks and AI applied to medical image data processing. In Computational Imaging V (Vol. 11396, p. 1139605). International Society for Optics and Photonics.

\item \custombold{Tahmassebi, A.}, Ehtemami, A., Mohebali, B., Gandomi, A. H., Pinker, K., \& Meyer-Baese, A. (2019, May). Big data analytics in medical imaging using deep learning. In Big Data: Learning, Analytics, and Applications (Vol. 10989, p. 109890E). International Society for Optics and Photonics.

\item \custombold{Tahmassebi, A.}, Mohebali, B., Meyer-Baese, L., Solimine, P., Pinker, K., \& Meyer-Baese, A. (2019, May). Determining driver nodes in dynamic signed biological networks. In Smart Biomedical and Physiological Sensor Technology XV (Vol. 11020, p. 110200A). International Society for Optics and Photonics.

\item \custombold{Tahmassebi, A.}, Mohebali, B., Solimine, P., Meyer-Baese, U., Pinker, K., \& Meyer-Baese, A. (2019, May). Model reduction of structural biological networks by cycle removal. In Smart Biomedical and Physiological Sensor Technology XV (Vol. 11020, p. 110200K). International Society for Optics and Photonics.

\item Mohebali, B., \custombold{Tahmassebi, A.}, Gandomi, A. H., \& Meyer-Baese, A. (2019, May). A big data inspired preprocessing scheme for bandwidth use optimization in smart cities applications using Raspberry Pi. In Big Data: Learning, Analytics, and Applications (Vol. 10989, p. 1098902). International Society for Optics and Photonics.

\item \custombold{Tahmassebi, A.} (2018, May). ideeple: Deep learning in a flash. In Disruptive Technologies in Information Sciences (Vol. 10652, p. 106520S). International Society for Optics and Photonics.

\item \custombold{Tahmassebi, A.}, Gandomi, A. H., McCann, I., Schulte, M. H., Goudriaan, A. E., \& Meyer-Baese, A. (2018, July). Deep Learning in Medical Imaging: fMRI Big Data Analysis via Convolutional Neural Networks. In Proceedings of the Practice and Experience on Advanced Research Computing (p. 85). ACM.


\item \custombold{Tahmassebi, A.}, Gandomi, A. H., \& Meyer-Baese, A. (2018, July). An Evolutionary Online Framework for MOOC Performance Using EEG Data. In 2018 IEEE Congress on Evolutionary Computation (CEC) (pp. 1-8). IEEE.\\

\item \custombold{Tahmassebi, A.}, Gandomi, A. H., \& Meyer-Baese, A. (2018, July). A Pareto Front Based Evolutionary Model for Airfoil Self-Noise Prediction. In 2018 IEEE Congress on Evolutionary Computation (CEC) (pp. 1-8). IEEE.\\

\item \custombold{Tahmassebi, A.}, Gandomi, A. H., McCann, I., Schulte, M. H., Schmaal, L., Goudriaan, A. E., \& Meyer-Baese, A. (2017, June). An evolutionary approach for fMRI big data classification. In Evolutionary Computation (CEC), 2017 IEEE Congress on (pp. 1029-1036). IEEE.\\


\item \custombold{Tahmassebi, A.}, Gandomi, A. H., \& Meyer-Bäse, A. (2017, July). High performance gp-based approach for fmri big data classification. In Proceedings of the Practice and Experience in Advanced Research Computing 2017 on Sustainability, Success and Impact (p. 57). ACM.

\item \custombold{Tahmassebi, A.}, Pinker-Domenig, K., Wengert, G., Lobbes, M., Stadlbauer, A., Romero, F. J., ... \& Meyer-Bäse, A. (2017, May). Dynamical graph theory networks techniques for the analysis of sparse connectivity networks in dementia. In Smart Biomedical and Physiological Sensor Technology XIV (Vol. 10216, p. 1021609). International Society for Optics and Photonics.


\item \custombold{Tahmassebi, A.}, Pinker-Domenig, K., Wengert, G., Lobbes, M., Stadlbauer, A., Wildburger, N. C., ... \& Botella, G. (2017, May). The driving regulators of the connectivity protein network of brain malignancies. In Smart Biomedical and Physiological Sensor Technology XIV (Vol. 10216, p. 1021605). International Society for Optics and Photonics.

\item \custombold{Tahmassebi, A.}, Amani, A. M., Pinker-Domenig, K., \& Meyer-Baese, A. (2018, March). Determining disease evolution driver nodes in dementia networks. In Medical Imaging 2018: Biomedical Applications in Molecular, Structural, and Functional Imaging (Vol. 10578, p. 1057829). International Society for Optics and Photonics.

\item \custombold{Tahmassebi, A.}, Ngo, D., Garcia, A., Castillo, E., Morales, D. P., Pinker-Domenig, K., ... \& Meyer-Bäse, A. (2018, May). Multi-level analysis of spatio-temporal features in non-mass enhancing breast tumors. In Smart Biomedical and Physiological Sensor Technology XV (Vol. 10662, p. 106620H). International Society for Optics and Photonics.

\item \custombold{Tahmassebi, A.}, Pinker-Domenig, K., Wengert, G., Helbich, T. H., Bago-Horvath, Z., Morris, E. A., \& Meyer-Baese, A. (2018). Radiomics with MRI for early prediction of the response to neo-adjuvant chemotherapy in breast cancer patients. Insights into Imaging, Springer.

\item \custombold{Tahmassebi, A.}, \& Buldum, A. (2015, March). Fluid flow calculations of Graphene Composites. In APS March Meeting Abstracts.

\item \custombold{Tahmassebi, A.}, Gandomi, A. H., McCann, I., Schulte, M. H., Schmaal, L., Goudriaan, A. E., \& Meyer-Baese, A. (2017). fMRI smoking cessation classification using genetic programming. In Workshop on Data Science meets Optimization.

\item Illan, I. A., \custombold{Tahmassebi, A.}, Ramirez, J., Gorriz, J. M., Foo, S. Y., Pinker-Domenig, K., \& Mayer-Baese, A. (2018, May). Machine learning for accurate differentiation of benign and malignant breast tumors presenting as non-mass enhancement. In Computational Imaging III (Vol. 10669, p. 106690W). International Society for Optics and Photonics.

\item McCann, I., \custombold{Tahmassebi, A.}, Foo, S. Y., Erlebacher, G., \& Meyer-Baese, A. (2018, April). NewsAnalyticalToolkit: an online natural language processing platform to analyze news. In Next-Generation Analyst VI (Vol. 10653, p. 106530P). International Society for Optics and Photonics.

\item Mohebali, B., \custombold{Tahmassebi, A.}, Gandomi, A. H., Meyer-Baese, A., \& Foo, S. Y. (2018, May). A scalable communication abstraction framework for internet of things applications using Raspberry Pi. In Disruptive Technologies in Information Sciences (Vol. 10652, p. 1065205). International Society for Optics and Photonics.



\item Yazicioglu, Y., \custombold{Tahmassebi, A.}, Pinker-Domenig, K., \& Meyer-Baese, A. (2018). Determining leader nodes in dementia networks. Insights into Imaging, Springer.


\item Pinker-Domenig, K., \custombold{Tahmassebi, A.}, Wengert, G., Helbich, T. H., Bago-Horvath, Z., Morris, E. A.,\& Meyer-Baese, A. (2018). Magnetic resonance imaging of the breast and radiomics analysis for an improved early prediction of the response to neoadjuvant chemotherapy in breast cancer patients.


\item Romero, F. J., Morales, D. P., Castillo, E., García, A.,  \custombold{Tahmassebi, A.}, \& Meyer-Baese, A. (2017, May). Reconfigurable wearable to monitor physiological variables and movement. In Smart Biomedical and Physiological Sensor Technology XIV (Vol. 10216, p. 1021608). International Society for Optics and Photonics.

\item Moradi Amani, A., Meyer-Baese, L., \custombold{Tahmassebi, A.}, \& Pinker-Domenig, K. (2019). Determining the best leader nodes in Alzheimer networks. Insights into Imaging, Springer.

\item Toral-Lopez, V., Criado, S., Romero, F. J., Morales, D. P., Castillo, E., García, A., \custombold{Tahmassebi, A.}, \& Meyer-Baese, A. (2018, May). Wearable biosignal acquisition system for decision aid. In Smart Biomedical and Physiological Sensor Technology XV (Vol. 10662, p. 106620F). International Society for Optics and Photonics.



\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\sectionsep 
\runsubsection{Conference Proceedings}
\sectionsep

\begin{itemize}

\item (2019). Big Data: Learning, Analytics, and Applications. In Proc. of SPIE Vol (Vol. 10989, pp. 1098901-1).

\item  (2018). Sensing for Agriculture and Food Quality and Safety X. In Proc. of SPIE Vol (Vol. 10665, pp. 1066501-1).

\item (2018). Disruptive Technologies in Information Sciences. Information Sciences, 1065201, 8.

\item (2018). Smart Biomedical and Physiological Sensor Technology XV. In Proc. of SPIE Vol (Vol. 10662, pp. 1066201-1).


\item (2017). Smart Biomedical and Physiological Sensor Technology XIV. In Proc. of SPIE Vol (Vol. 10216, pp. 1021601-1).

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5


\section{Awards} 
\sectionsep
\begin{tabular}{llll}
\textbullet{} August & 2019	  & Cerner Corporation Q2 All Star Award \\

\textbullet{} April & 2018	  & Florida State University Research \& Creativity Award, Amount = \$1000    \\

\textbullet{} March &2018	  & ONR Gulf of Mexico Summer School Grant, Amount = \$2400    \\

\textbullet{} January& 2018	  & Nominated for SPIE Medical Imaging Best Student Paper Award  \\

\textbullet{} January& 2018	  & Florida State University Congress of Graduate Students Travel Grant, Amount = \$200   \\
 
\textbullet{} January &2018      &  SPIE Travel Grant, Department of Scientific Computing, Amount = \$600\\

\textbullet{} July &2017      & Tutorial Volunteer MVP Award, [PEARC2017]\\

\textbullet{} July& 2017	  & Florida State University Congress of Graduate Students Travel Grant, Amount = \$1400\\

\textbullet{} June& 2017	  & [PEARC2017] Travel Grant, Google, Amount = \$1400\\

\textbullet{} April& 2017	  & SPIE Travel Grant, Department of Scientific Computing, Amount = \$1200\\

\textbullet{} April& 2017	  & Florida State University Congress of Graduate Students Travel Grant, Amount = \$200  \\

\textbullet{} January& 2017	  & PhD Candidacy Exam (Score : 95.1\%), Department of Scientific Computing  \\

\textbullet{} July& 2016	  & Florida State University Congress of Graduate Students Travel Grant, Amount = \$200  \\

\textbullet{} July& 2016	  & 1st Place in [XSEDE2016] Data Simulation \& Modeling Contest  \\

\textbullet{} June & 2016	  & [XSEDE2016] Travel Grant, Texas Advanced Computing Center (TACC), Amount = \$3000\\

\textbullet{} October& 2015	  & Dean's Scholarship, Florida State University, Amount = \$1000\\

\textbullet{} August& 2015	 & Graduate Teaching Assistantship, Florida State University\\

\textbullet{} December& 2014	  & Annual Outstanding MS Academic Achievement, The University of Akron, Amount = \$500\\

\textbullet{} December& 2013	 & Annual Outstanding MS Academic Achievement, The University of Akron, Amount = \$500 \\

\textbullet{} August& 2013	 & Graduate Teaching Assistantship, The University of Akron

\end{tabular}
\sectionsep




\sectionsep
\hline
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\begin{minipage}[t]{\textwidth}
\location{Fluent:}
Python \textbullet{} SQL \textbullet{} dbt \textbullet{} Scikit-Learn\textbullet{} Pandas \textbullet{} ZenML \textbullet{} MLFlow \textbullet{} Kubeflow \textbullet{} Dash &\ Streamlit \textbullet{} Git \textbullet{} GitHub \textbullet{} GitLab \\
\location{Experienced:}
PySpark \& MLlib \textbullet{} C/C++ \textbullet{} SAS \textbullet{} Fortran \textbullet{} MPI \textbullet{} OpenMP   \textbullet{} CUDA \textbullet{} OpenACC   \textbullet{} MATLAB \textbullet{} Hadoop \textbullet{}  HTML \& CSS
\sectionsep
\end{minipage}




\sectionsep
\hline
\sectionsep

\section{Certifications} 
% \sectionspace % Some whitespace after the section

\begin{tabular}{rll}

2018 & Advanced SQL for Data Scientists & License: 9EB75CADFCDF4297BBF41E89BE70DB6F \\
2018 & Learning SQL Programming & License: 328A2E0E68F84AEE8142601459F900D2\\
2018 & Linux Command Line & License: BAE1FAFC35964CF08DF99E1EC6519E0C\\

2018 & Apache Spark Essential Training & License: AX-eCJJ-IO4kqPsW9qq\_CDkbgLvl\\

2018 & Four Semesters of Computer Science in 5 Hours & License: ARfNGq4Nst4o2JfaxfyeD6DWaMzX\\


2018 & Python for Data Science Tips, Tricks, \& Techniques & License: AXt4gbz9bsM1bKfLB3UVtpHhWyMm\\

2018 & Statistics Foundations: 1 & License: AWmWedX96Hqqr8gcMt5UYvHgFScx \\

2018 & Statistics Foundations: 2 & License Ab63cjgN21FxLchWLQvabSyXH\_ca \\

2018 & Statistics Foundations: 3 & License Adk4NpfQ23tQGFnaZ7WkV-YFpcfO \\




2016 &  SAS Certified Advanced Programmer for SAS 9 &

\textbf{\href{https://people.sc.fsu.edu/~at15b/Achievements/SAS-ADVANCED.pdf}{License: AP018225v9}}\\

2016 &  SAS Certified Base Programmer for SAS 9 & \textbf{\href{https://people.sc.fsu.edu/~at15b/Achievements/SAS-BASE.pdf}{License: BP060504v9}}\\

2016 & The Data Scientist's Toolbox &
\textbf{\href{https://people.sc.fsu.edu/~at15b/Achievements/DataScientist.pdf}{License: ZW45KTLYBXK5}}

\end{tabular}

\sectionsep




\sectionsep
\hline
\sectionsep

\section{Societies} 

APS \textbullet{}  SPIE \textbullet{} ACM \textbullet{} IEEE \textbullet{} Elsevier \textbullet{} Frontiers



\sectionsep
\hline
\sectionsep

\section{Editorial Board} 
\begin{itemize}
\item Associate Editor at Journal of Frontiers in Neuroinformatics
\end{itemize}

\section{Peer Reviews}
\begin{itemize}
\item Journal of Neurocomputing, Elsevier
\item European Journal of Radiology, Elsevier
\item IEEE Congress of Evolutionary Computations (CEC)
\item Magnetic Resonance in Medicine, Wiley
\item International Journal of Data Science and Analysis
\item Current Journal of Applied Science and Technology
\item Asian Journal of Research in Computer Science
\item Journal of Neural Computing and Applications (NCAA)
\item International Journal of Mechatronics, Electrical \& Computer Technology (IJMEC)
\end{itemize}







\end{document}  \documentclass[]{article}